paper_code_documentation

### 2020-10-04 outputs/documents/notes/paper_code_documentation.Rmd
paper code trials

Extra step
pip install nltk

>>>>

## Paper: Enabling Language Models to Fill in the Blanks

Published date: September 10, 2020

Authors: Chris Donahue, Mina Lee, Percy Liang

Affiliation: Stanford University

Code URL: https://github.com/chrisdonahue/ilm

Not able to follow through the code tutorial from Github. Google Collab code generates demo successfully.

## Steps for Github repo

1. Download the code and initialize

``` {python, eval = FALSE}
git clone git@github.com:chrisdonahue/ilm.git
cd ilm
pip install -r requirements.txt
python -c "import nltk; nltk.download('punkt')"
pip install -e .
```

You might have to run extra code to install required packages if you don't have them already. In my case, I had to get `nltk`.

``` {python, eval = FALSE}
pip install nltk
```

2. The following script was provided to download training dataset and create training examples:

``` {sh, eval = FALSE}
DATASET=arxiv_cs_abstracts

pushd data
./get_${DATASET}.sh
popd

for SPLIT in train valid
do
	python create_ilm_examples.py \
		${SPLIT} \
		data/char_masks/${DATASET} \
		--seed 0 \
		--data_name ${DATASET} \
		--data_split ${SPLIT}
done
```

The above code was saved as a sh script and execute by the following command in the terminal:

``` {python, eval = FALSE}
./script.sh
```

And the above execution raised an error:

``` {python, eval = FALSE}
~/desktop/repos/ilm/data ~/desktop/repos/ilm
~/desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts ~/desktop/repos/ilm/data ~/desktop/repos/ilm
./get_arxiv_cs_abstracts.sh: line 5: wget: command not found
sed: illegal option -- r
usage: sed script [-Ealn] [-i extension] [file ...]
       sed [-Ealn] [-i extension] [-e script] ... [-f script_file] ... [file ...]
./get_arxiv_cs_abstracts.sh: line 5: wget: command not found
gunzip: can't stat: arxiv_cs_abstracts.txt.gz (arxiv_cs_abstracts.txt.gz.gz): No such file or directory
./get_arxiv_cs_abstracts.sh: line 7: sha256sum: command not found
~/desktop/repos/ilm/data ~/desktop/repos/ilm
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
(project_ilm) (base) Kelis-MacBook-Pro:ilm kelichiu$ ./script.sh
~/desktop/repos/ilm/data ~/desktop/repos/ilm
./script.sh: line 4: data/get_arxiv_cs_abstracts.sh: No such file or directory
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
(project_ilm) (base) Kelis-MacBook-Pro:ilm kelichiu$ ./script.sh
~/desktop/repos/ilm/data ~/desktop/repos/ilm
./script.sh: line 4: data/get_arxiv_cs_abstracts.sh: No such file or directory
~/desktop/repos/ilm
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'
Traceback (most recent call last):
  File "create_ilm_examples.py", line 158, in <module>
    limit=args.max_num_documents)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 24, in get_dataset
    d = arxiv_cs_abstracts(split, *args, data_dir=data_dir, **kwargs)
  File "/Users/kelichiu/Desktop/repos/ilm/ilm/datasets.py", line 63, in arxiv_cs_abstracts
    with open(os.path.join(data_dir, 'arxiv_cs_abstracts.txt'), 'r') as f:
FileNotFoundError: [Errno 2] No such file or directory: '/Users/kelichiu/Desktop/repos/ilm/data/raw_data/arxiv_cs_abstracts/arxiv_cs_abstracts.txt'

```

## Google Colab

Link: https://colab.research.google.com/drive/1So95M0hHefyNm_eELglCna_ZayoDX6KV?usp=sharing

### Input

``` {txt, eval = FALSE}
English Class

Christie was good at doing _. _ _ _ She ended up failing the test.
```

### Encode

``` {txt, eval = FALSE}
English Class

Christie was good at doing<|infill_word|>.<|infill_paragraph|><|infill_sentence|>
  <|infill_sentence|> She ended up failing the test.
```

### Output

``` {txt, eval = FALSE}
English Class

Christie was good at doing things. One day at the library she had to take a math test. 
She made a terrible grade. Christie felt terrible and did it anyways. 
She ended up failing the test.

English Class

Christie was good at doing homework. She would stay up late to study. 
When she was home for class, she would go into and out of class. 
But her teacher couldn't find her anywhere. She ended up failing the test.
```
